Why robot programming is hard

### 2013-11-20 paper.tex
Final version as submitted

\title {Why robot programming is hard}
\author {Tessa Lau \\
Willow Garage \\
Menlo Park, CA USA \\
{\tt tlau@willowgarage.com}
}
\maketitle

@@

What I have found is that the problem is not that robots {\em cannot} do what we want them to do. The problem is that it is too difficult to {\em tell} robots what we want them to do. Robot control can be roughly categorized into three distinct phases: direct demonstration, tele-operation (or teleop for short), and higher-level programming.

In demonstrational interfaces, a human operator moves a robot through a series of positions to demonstrate the motion it should perform. The robot then continues to perform this motion unattended. This style of programming is common for industrial robots, which can be programmed to move items around on conveyor belts or do precise assembly tasks. Demonstrational interfaces are typically limited to repeating only what was previously demonstrated, in the worst case performing the exact same motion down to the millimeter regardless of whether the part is in the same place as it was last time.

@@

Both demonstration and teleop suffer the limitation that a human operator must be immediately in the loop while the robot is operating. To make robots useful in the home, they will need to function {\em autonomously}, which leads to the notion of robot programming: giving high-level directives to robots so that they can function on their own without direct human guidance.  A full programming solution will likely involve a blend of different techniques including demonstration, teleop, and autonomous subroutines. For example, a task of setting the dinner table may include a high-level program of fetching silverware from the kitchen and placing it on the dining table, a demonstration of how to open this particular silverware drawer, and teleoperation when something goes awry (such as the silverware drawer being empty).

For personal robotics to truly succeed, robot programming will need to be simple enough that non-experts can do it.

@@

\begin{figure*}[tbh]
\center\scalebox{0.20}{\includegraphics{rviz.png}}
\caption{RViz interface for robot visualization}
\label{rviz}
\end{figure*}

However, ROS provides a fairly low-level interface to robot control. Designed for roboticists, the RViz interface (Figure~\ref{rviz}) displays all the sensor feeds coming from the robot and lets one send low-level motion commands to the robot such as rolling forward or rotating the shoulder joint. In the figure, a robot is shown examining objects on a table in front of it. The green pattern represents the data from a depth sensor mounted on the robot's head, whereas the purple line represents the walls detected by a laser rangefinder mounted on the robot's base. The tricolored axes display the various coordinate frames in use, and the gray floor displays the map the robot uses for navigation. (TODO: display costmaps, TF axes)

@@

Yet positioning an arm through direct manipulation or teleop is relatively easy compared to doing it programmatically. In order to program an arm, one must first specify {\em where} it should go.  Expert roboticists represent the world in terms of {\em reference frames} (coordinate systems that are defined relative to a fixed position). For example, one reference frame could be relative to the building, with the front door being at coordinate (0, 0).  Other reference frames are defined relative to stationary parts of the robot, such as its base (if it is on wheels), the head-mounted camera, or the right elbow joint.

Sending an arm to a specific position is useful for robot tasks such as, for example, looking at what it is holding by moving its hand to half a meter in front of its face. This half-meter is most reliably specified in the reference frame relative to the robot's head. Given this goal position, the programmer must find a series of arm configurations that moves the arm to the desired place, while avoiding contact with obstacles in the environment.

@@

This past generation of commercial home robots illustrates one extreme end of the simplicity versus expressiveness tradeoff. iRobot's successful Roomba line of vacuum-cleaning robots\footnote{http://www.irobot.com/us/learn/home/roomba.aspx} sports a single-button interface that simply says ``Clean''. While the robot will eventually clean your floors, you lose control over how exactly it does so, as it performs what seems like a random walk through your home.

@@

@@

>>>>

\title {Why robot programming is hard}
\author {Tessa Lau \\
Affiliation TBD \\
Buenos Aires, Argentina \\
{\tt tlau@tlau.org}
}
\maketitle

@@

What I have found is that the problem is not that robots {\em cannot} do what we want them to do. The problem is that it is too difficult to {\em tell} robots what we want them to do. Even basic robot use entails some form of programming, because autonomous algorithms are not yet reliable and robust enough to complete useful tasks. Except in a few narrow domains where automation has become robust and practical, the mere act of telling a robot what to do involves a complex set of skills.

Robot control can be roughly categorized into three distinct phases: direct demonstration, tele-operation (or teleop for short), and end user programming.

In demonstrational interfaces, a human operator moves a robot through a series of positions to demonstrate the motion it should perform. The robot then continues to perform this motion unattended. This style of programming is common for industrial robots, which can be programmed to move items around on conveyor belts or do precise assembly tasks. Demonstrational interfaces are typically limited to repeating only what was previously demonstrated, performing the exact same motion down to the millimeter. While this is useful in controlled environments such as factories, typical home environments are much more fluid and changing. Simply repeating a previous motion a second time may not produce the desired effect.

@@

Teleop suffers from the limitation that a human operator must be immediately in the loop while the robot is operating. To make robots useful in the home, they will need to function {\em autonomously}, which leads to the notion of end user programming: giving high-level directives to robots so that they can function on their own without direct human guidance.  A full programming solution will likely involve a blend of different techniques including demonstration, teleop, and autonomous subroutines. For example, a task of setting the dinner table may include a high-level program of fetching silverware from the kitchen and placing it on the dining table, a demonstration of how to open this particular silverware drawer, and teleoperation when something goes awry (such as the silverware drawer being empty).

For personal robotics to truly succeed, regular people will need to use robot programming interfaces to tell robots what to do. These interfaces for robot programming will need to be simple enough for ordinary consumers to be able to pick up and use. In this article I detail some of the challenges that make robot control such an inherently difficult problem.

@@

\begin{figure*}[tbh]
\center\scalebox{0.13}{
	\includegraphics{rviz1.png}
	\includegraphics{rviz2.png}
}
\caption{RViz interfaces for robot visualization}
\label{rviz}
\end{figure*}

However, ROS provides a fairly low-level interface to robot control. Designed for roboticists, the RViz interface (Figure~\ref{rviz}) displays all the sensor feeds coming from the robot and lets one send low-level motion commands to the robot such as rolling forward or rotating its shoulder joint. The figure shows two different perspectives on the same robot examining objects on a table in front of it. The left figure shows a third-person view of the robot and the table, rendered on top of a two-dimensional map of its environment (the gray pattern in the background). The green overlays on top of the tabletop objects indicate that they are recognized by the system as objects that can be picked up. The yellow grid pattern indicates horizontal surfaces that are detected, such as the floor.  The right figure shows the view as soon from the robot's head-mounted camera. The red/green/blue arrows are control markers that can be used to rotate and move the robot's gripper in all directions.

@@

% Yet positioning an arm through direct manipulation or teleop is relatively easy compared to doing it programmatically. In order to program an arm, one must first specify {\em where} it should go.  Expert roboticists represent the world in terms of {\em reference frames} (coordinate systems that are defined relative to a fixed position). For example, one reference frame could be relative to the building, with the front door being at coordinate (0, 0).  Other reference frames are defined relative to stationary parts of the robot, such as its base (if it is on wheels), the head-mounted camera, or the right elbow joint.
% 
% Sending an arm to a specific position is useful for robot tasks such as, for example, looking at what it is holding by moving its hand to half a meter in front of its face. This half-meter is most reliably specified in the reference frame relative to the robot's head. Given this goal position, the programmer must find a series of arm configurations that moves the arm to the desired place, while avoiding contact with obstacles in the environment.

@@

The current generation of commercial home robots illustrates one extreme end of the simplicity versus expressiveness tradeoff. iRobot's successful Roomba line of vacuum-cleaning robots\footnote{http://www.irobot.com/us/learn/home/roomba.aspx} sports a single-button interface that simply says ``Clean''. While the robot will eventually clean your floors, you lose control over how exactly it does so, as it performs what seems like a random walk through your home.

@@

% Acknowledgements
% Andreas Paepke
% Kaijen Hsiao
% Matei Ciocarlie

@@

% vim: set lbr:
